Initial Analysis

### 2020-07-30 Scripts/Initial_Analysis.Rmd
New Fig1!

  ####### For testing ###

  gc()

  plot_all <- ggdraw() +
  # map
  draw_plot(Map, x = 0, y = 0.45, width = 1, height = 0.58) +
  draw_plot_label(label = c("A", "B"), 
                  size = 20,
                  x = c(0, 0), 
                  y = c(1, 0.45)
  )

  save_plot(
    "Map.png",
    plot_all,
    base_height = 8,
    base_width = 8
  )

  #######

  Map <- ggplot() +
    geom_sf(data = World_sf_si_land,
            aes(fill = reorder(Bins_Plot,Value)), 
            colour = "grey80",
            size = 0.1) +
    geom_sf(data = World_sf_si,
            aes(fill =  reorder(Bins_Plot,n_trans_spp)),
            colour = "grey20",
            size = 0.1) + # n_trans_spp or Bins
    geom_sf(data = Grey_land,aes(fill = Bins),fill = "grey80", colour = "grey50",size = 0.1) + # n_trans_spp or Bins
    scale_fill_manual("",values = c("#5BBCD6",#"#5BBCD6", # blue
                                    "#00A08A",#"#00A08A", #green
                                    "#F2AD00",#"#F2AD00", # Yellow
                                    "#F98400",#"#F98400", #Orange
                                    "#FF0000"#,"#FF0000" #Red
    ),
    na.translate = F
    ) +
    ggtheme_map() +
    # Transboundary labels
    annotate("text", 
             # x =(c(-85.5,-30,25,81,136)+5),
             # y = -93.5,
             x =(c(-8500000,-3000000,2500000,7500000,12800000)),
             y = -9050000,
             label = Labels_Trans, 
             color="black", 
             size=3, 
             angle=0, 
             # fontface="bold",
             hjust=0) +
    # Revenue labels
    annotate("text",
             # x =(c(-85.5,-31,20,75,131)+5),
             # y = -110,
             x =(c(-8500000,-3200000,2000000,7000000,12500000)),
             y = -11000000,
             label = Labels,
             color="black",
             size=3,
             angle=0,
             # fontface="bold",
             hjust=0) +
    # Legend Titles
    annotate("text", 
             # x =-180,
             # y = -93.5,
             x =-17000000,
             y = -9050000,
             label = "Transboundary Spp. (n)", 
             color="black", 
             size=3, 
             angle=0, 
             fontface="bold",
             hjust=0) +
    annotate("text", 
             # x =-180,
             # y = -110,
             x =-17000000,
             y = -11000000,
             label = Map_Label,
             color="black", 
             size=3, 
             angle=0, 
             fontface="bold",
             hjust=0) +
    theme(
      legend.box.margin = margin(t = -55, l = 120),
      legend.text = element_blank(),
    ) +
    guides(fill = guide_legend(nrow = 1))

@@

  Rev_Plot <- ggplot(
    # Regional plots
    data = Subregion_Rev_Data,
    aes(
      x=reorder(id,Value_sum),
      y=Value_sum, 
      fill=Value_sum
    )
  ) +    
    ylim(-1500, max_Rev_lim) +
    geom_bar(stat="identity") +
    # Regional averages
    geom_point(data = Subregion_Rev_Data,
               aes(
                 x=reorder(id,Value_sum),
                 y=Value_m
               ),
               colour = "black",
               alpha = 0.5
    ) +
    # Regional sds
    geom_errorbar(data = Subregion_Rev_Data,
                  aes(
                    ymin=ifelse(Value_m-Value_sd <= 0,0,Value_m-Value_sd), # sets lower to 0
                    ymax=Value_m+Value_sd
                  ), 
                  width=.2,
                  position=position_dodge(.9),
                  alpha = 0.5) +
    # Looking good
    theme_minimal() +
    theme(
      legend.position = c(0.73,0.60),
      axis.text = element_blank(),
      axis.title = element_blank(),
      panel.grid = element_blank(),
      plot.margin = margin(0,-10,-6,-10,"cm")
    )  +
    # Base line
    # geom_segment(aes(x = 1, y = 1, xend = 17, yend = 17),  
    #              colour = "black", size=0.1, inherit.aes = FALSE) +
    coord_polar(start = 0) + 
    geom_text(data=label_data_rev, 
              aes(x=id,
                  y=Value_sum,
                  label=sub_region,
                  hjust=hjust), 
              color="black",
              fontface="bold",
              size=2, 
              angle= label_data_rev$angleb, 
              inherit.aes = FALSE) +
    scale_fill_gradientn("",
                         colours = pal,
                         limits = c(0,12000),
                         breaks = seq(0,12000,3000)) +
    guides(fill = guide_colorbar(label.position = "left")
    )

@@

  Catch_Plot <- ggplot(data = Subregion_Catch_Data,
                     aes(x=reorder(id,Value_sum),
                         y=Value_sum, 
                         fill=Value_sum
                     )
) +    
  ylim(-1.5, max_Catch_lim) +
  geom_bar(stat="identity") +
  # Regional averages
  geom_point(data = Subregion_Catch_Data,
             aes(
               x=reorder(id,Value_sum),
               y=Value_m
             ),
             colour = "black",
             alpha = 0.5
  ) +
  # Regional sd's
  geom_errorbar(data = Subregion_Catch_Data,
    aes(
      ymin=ifelse(Value_m-Value_sd <= 0,0,Value_m-Value_sd),
      ymax=Value_m+Value_sd
    ), 
    width=.2,
    position=position_dodge(.9),
    alpha = 0.5) +
  theme_minimal() +
  theme(
    legend.position = c(0.1,0.60),
    axis.text = element_blank(),
    axis.title = element_blank(),
    panel.grid = element_blank(),
    plot.margin = margin(0,-10,-6,-5,"cm")
  )  +
  # Base line
  # geom_segment(aes(x = 0, y = 1, xend = 17, yend = 17),
  #              colour = "black", size=0.1, inherit.aes = FALSE) +
  coord_polar(start = 0) + 
  geom_text(data=label_data_catch, 
            aes(x=id,
                y=ifelse(Value_sum >= 12,12,Value_sum+0.1), # Fix names overlap
                label=sub_region,
                hjust=hjust), 
            color="black",
            fontface="bold",
            size=2, 
            angle= label_data_catch$angleb, 
            inherit.aes = FALSE) +
  scale_fill_gradientn("",
                       limits = c(0,12),
                       breaks = seq(0,12,3),
                       colours = pal
  )

@@

  save_plot(
    # paste(Figures_Path,"100_25_Bins_Value_Region.png",sep=""),
    Plot_Name,
    plot_all,
    base_height = 8,
    base_width = 8
  )

@@

@@

SAU_Tim_Data <- fread(paste(my_path("D"),"Distribution/sau_catch_value_country_taxon_JEPA.csv", sep ="")) #%>% 
  # mutate(value = value*1.62)

@@

# Read Species Status Data (Sub-routine Species Status)
Status_Data <- fread(paste(my_path("R"),"EEZ/Species_Status.csv", sep ="")) %>% 
  clean_names() %>% 
  rename(sf_eez_name=territory)

@@

Clean_Results_Trans <- fread(paste(my_path("R"),"/EEZ/Clean_Results_Trans.csv", sep ="")) %>%
  mutate(fishing_entity = ifelse(eez_name == "Spain (Mediterranean and Gulf of Cadiz)","Spain",paste(fishing_entity)))

@@

# Set manual breaks for bins
Map_Breaks <- c(-1,10,100,1000,5000,10000)

@@

Value_Trans_Country <- sau_eez_fes %>% 
  group_by(fishing_entity_id, fishing_entity) %>% 
  summarise(n=n()) %>% # Get all of the fishing entity and id
  select(-n) %>% 
  left_join(Tresholded_T_Data,
            by = "fishing_entity") %>% 
  group_by(fishing_entity_id,
           fishing_entity,
           taxon_key) %>% 
  summarise(n()) %>% # get each taxa per nation
  left_join(SAU_Sampled_Data,
            by = c("fishing_entity_id","taxon_key")) %>% 
  group_by(fishing_entity,Variable) %>% # Estimate the amount of dollars of each nation 
  summarise(
    Trans_Entity_n = length(unique(taxon_key)),
    Trans_Total = sum(Value,na.rm=T), #million
  ) %>%
  ungroup() %>%
  filter(!is.na(Variable)) %>%
  mutate(
    Trans_Total = ifelse(Variable == "value",Trans_Total/1000000, #million
                         ifelse(Variable == "catch",Trans_Total/1000, #thousand
                                Trans_Total)
                         )
  ) %>% 
  spread(Variable,Trans_Total) %>% 
  left_join(Entity_Area, 
            by = "fishing_entity") %>% 
  # Include the weighted method for supplementals
  mutate_at(
    vars(catch,value),
    funs(weight= ./(Size_Entity/1000000))
  ) %>% 
  gather("Variable","Value",catch:value,catch_weight:value_weight) %>% 
  group_by(fishing_entity,Variable,Value) %>% 
  mutate(
    Bins = cut(Value, breaks = Map_Breaks, dig.lab = 5),
    Bins_Plot = cut(Value, breaks = Map_Breaks,
                    labels = c('super low', 'low','median','high','super high'),
                    dig.lab = 5 # Removes scientific notaion
    )
  ) %>% 
  left_join(Total_Value_EEZ,
            by = c("fishing_entity", "Variable") 
            ) %>% # uncomment for estimating percentage
  # Convert catch to million tonnes
  ungroup() %>% 
  mutate(
    Value = ifelse(Variable == "catch",Value/1000, #million
                         Value),
    Trans_Per = (Value/Total_Value)*100000000 #Return to percentage
  )

@@

Subregion_Trans_raw_Value <- Value_Trans_Country %>% 
  left_join(UN_Regions,
            by = "fishing_entity") %>% 
  mutate(sub_region = ifelse(is.na(sub_region), "Other",paste(sub_region))) %>% 
  group_by(sub_region,Variable) %>% 
  summarise_if(is.numeric,c(sum = sum,
                            m = mean,
                            sd = sd),
               na.rm=T) %>%
  # select(-Size_Entity,-Trans_Entity_n) %>% 
  arrange(Variable) %>%
  ungroup() %>% 
  mutate(id = rep(seq(1,17),4)) %>% 
  mutate(Value_sum=ifelse(Variable == "catch" & Value_sum >= 12,12,Value_sum))

@@

Status_Plot_Data <- tibble(
  fishing_entity = rep(unique(Status_Data_Plot$individual),4),
  observation = rep(unique(Status_Data_Plot$observation),153)
) %>% 
  left_join(UN_Regions) %>% 
  rename(individual = fishing_entity) %>% 
  full_join(Status_Data_Plot,
            by = c("individual","observation")
  ) %>% 
  mutate(value = ifelse(is.na(value),0,value)#,
         # group = ifelse(is.na(group),"Other",group)
  ) %>% 
  select(individual,observation,group=georegion,value) %>% 
  filter(group != "other")

@@

ggsave(
  plot = last_plot(),
  width = 17,
  height = 15,
  units = "in",
  # filename = "Plot.png"
  filename = "Territory_circular_status.png",
  path = Figures_Path
)

>>>>

  Map <- ggplot() +
    geom_sf(data = World_sf_si_land,
            aes(fill = reorder(Bins_Plot,Value)), 
            colour = "grey80",
            size = 0.1) +
    geom_sf(data = World_sf_si,
            aes(fill =  reorder(Bins_Plot,n_trans_spp)),
            colour = "grey20",
            size = 0.1) + # n_trans_spp or Bins
    geom_sf(data = Grey_land,aes(fill = Bins),fill = "grey80", colour = "grey50",size = 0.1) + # n_trans_spp or Bins
    scale_fill_manual("",values = c("#5BBCD6",#"#5BBCD6", # blue
                                    "#00A08A",#"#00A08A", #green
                                    "#F2AD00",#"#F2AD00", # Yellow
                                    "#F98400",#"#F98400", #Orange
                                    "#FF0000"#,"#FF0000" #Red
    ),
    na.translate = F
    ) +
    ggtheme_map() +
    # Transboundary labels
    annotate("text", 
             # x =(c(-85.5,-30,25,81,136)+5),
             # y = -93.5,
             x =(c(-8500000,-3000000,2500000,7500000,12800000)),
             y = -9050000,
             label = Labels_Trans, 
             color="black", 
             size=3, 
             angle=0, 
             # fontface="bold",
             hjust=0) +
    # Revenue labels
    annotate("text",
             # x =(c(-85.5,-31,20,75,131)+5),
             # y = -110,
             x =(c(-8500000,-3200000,2000000,7000000,12500000)),
             y = -11000000,
             label = Labels,
             color="black",
             size=3,
             angle=0,
             # fontface="bold",
             hjust=0) +
    # Legend Titles
    annotate("text", 
             # x =-180,
             # y = -93.5,
             x =-17000000,
             y = -9050000,
             label = "Transboundary Spp. (n)", 
             color="black", 
             size=3, 
             angle=0, 
             fontface="bold",
             hjust=0) +
    annotate("text", 
             # x =-180,
             # y = -110,
             x =-17000000,
             y = -11000000,
             label = Map_Label,
             color="black", 
             size=3, 
             angle=0, 
             fontface="bold",
             hjust=0) +
    theme(
      legend.box.margin = margin(t = -58, l = 120),
      legend.text = element_blank(),
    ) +
    guides(fill = guide_legend(nrow = 1))

@@

  Rev_Plot <- ggplot(
    # Regional plots
    data = Subregion_Rev_Data,
    aes(
      x=reorder(id,Value_sum),
      y=Value_sum, 
      fill=Value_sum
    )
  ) +    
    ylim(-1500, max_Rev_lim) +
    geom_bar(stat="identity") +
    # Regional averages
    geom_point(data = Subregion_Rev_Data,
               aes(
                 x=reorder(id,Value_sum),
                 y=Value_m
               ),
               colour = "black",
               alpha = 0.5
    ) +
    # Regional sds
    geom_errorbar(data = Subregion_Rev_Data,
                  aes(
                    ymin=ifelse(Value_m-Value_sd <= 0,0,Value_m-Value_sd), # sets lower to 0
                    ymax=Value_m+Value_sd
                  ), 
                  width=.2,
                  position=position_dodge(.9),
                  alpha = 0.5) +
    # Looking good
    theme_minimal() +
    theme(
      legend.position = c(0.73,0.60),
      axis.text = element_blank(),
      axis.title = element_blank(),
      panel.grid = element_blank(),
      plot.margin = margin(0,-10,-6,-10,"cm")
    )  +
    # Base line
    # geom_segment(aes(x = 1, y = 1, xend = 17, yend = 17),  
    #              colour = "black", size=0.1, inherit.aes = FALSE) +
    coord_polar(start = 0) + 
    geom_text(data=label_data_rev, 
              aes(x=id,
                  y=Value_sum,
                  label=sub_region,
                  hjust=hjust), 
              color="black",
              fontface="bold",
              size=2, 
              angle= label_data_rev$angleb, 
              inherit.aes = FALSE) +
    scale_fill_gradientn("",
                         colours = pal,
                         limits = c(0,14000),
                         breaks = seq(0,14000,3500)
                         ) +
    guides(fill = guide_colorbar(label.position = "left")
    );Rev_Plot

@@

  Catch_Plot <- ggplot(data = Subregion_Catch_Data,
                     aes(x=reorder(id,Value_sum),
                         y=Value_sum, 
                         fill=Value_sum
                     )
) +    
  ylim(-1.5, max_Catch_lim) +
  geom_bar(stat="identity") +
  # Regional averages
  geom_point(data = Subregion_Catch_Data,
             aes(
               x=reorder(id,Value_sum),
               y=Value_m
             ),
             colour = "black",
             alpha = 0.5
  ) +
  # Regional sd's
  geom_errorbar(data = Subregion_Catch_Data,
    aes(
      ymin=ifelse(Value_m-Value_sd <= 0,0,Value_m-Value_sd),
      ymax=Value_m+Value_sd
    ), 
    width=.2,
    position=position_dodge(.9),
    alpha = 0.5) +
  theme_minimal() +
  theme(
    legend.position = c(0.1,0.60),
    axis.text = element_blank(),
    axis.title = element_blank(),
    panel.grid = element_blank(),
    plot.margin = margin(0,-10,-6,-5,"cm")
  )  +
  # Base line
  # geom_segment(aes(x = 0, y = 1, xend = 17, yend = 17),
  #              colour = "black", size=0.1, inherit.aes = FALSE) +
  coord_polar(start = 0) + 
  geom_text(data=label_data_catch, 
            aes(x=id,
                y=ifelse(Value_sum >= 12,12,Value_sum+0.1), # Fix names overlap
                label=sub_region,
                hjust=hjust), 
            color="black",
            fontface="bold",
            size=2, 
            angle= label_data_catch$angleb, 
            inherit.aes = FALSE) +
  scale_fill_gradientn("",
                       limits = c(0,12),
                       breaks = seq(0,12,3),
                       colours = pal
  );Catch_Plot

@@

  gc()
  save_plot(
    # paste(Figures_Path,"100_25_Bins_Value_Region.png",sep=""),
    Plot_Name,
    plot_all,
    base_height = 8,
    base_width = 8
  )

@@

# World_sf %>% filter(str_detect(eez_name, "Cu"))

@@

SAU_Tim_Data <- fread(paste(my_path("D"),"Distribution/sau_catch_value_country_taxon_JEPA.csv", sep ="")) %>%
  mutate(value = 1.16 * value)

@@

# Read Species Status Data (Sub-routine Species Status)
Status_Data <- fread(paste(my_path("R"),"EEZ/Species_Status.csv", sep ="")) %>% 
  clean_names() %>% 
  rename(eez_name=territory) %>% 
  mutate(eez_name = ifelse(eez_name == "Spain (Mediterranean and Gulf of Cadiz)","Spain",eez_name)
         )

@@

Clean_Results_Trans <- fread(paste(my_path("R"),"/EEZ/Clean_Results_Trans.csv", sep ="")) %>% 
  mutate(eez_name = ifelse(eez_name == "Cote dIvoire","Côte d'Ivoire",
                           ifelse(eez_name == "Curacao (Netherlands)","Curaçao (Netherlands)",eez_name)
                           ),
         fishing_entity = ifelse(fishing_entity == "Cote dIvoire","Côte d'Ivoire",
                                 ifelse(fishing_entity == "Curacao (Netherlands)","Curaçao (Netherlands)",fishing_entity))
         )

@@

# Set manual breaks for bins
Map_Breaks <- c(-1,10,100,1000,2000,12000) 
# Map_Breaks <- c(-1,20,200,2000,1000,20000)

@@

Value_Trans_Country <- sau_eez_fes %>% 
  group_by(fishing_entity_id, fishing_entity) %>% 
  summarise(n=n()) %>% # Get all of the fishing entity and id
  select(-n) %>% 
  left_join(Tresholded_T_Data,
            by = "fishing_entity") %>% 
  group_by(fishing_entity_id,
           fishing_entity,
           taxon_key) %>% 
  summarise(n()) %>% # get each taxa per nation
  left_join(SAU_Sampled_Data,
            by = c("fishing_entity_id","taxon_key")) %>% 
  group_by(fishing_entity,Variable) %>% # Estimate the amount of dollars of each nation 
  summarise(
    Trans_Entity_n = length(unique(taxon_key)),
    Trans_Total = sum(Value,na.rm=T), #million
  ) %>%
  ungroup() %>%
  filter(!is.na(Variable)) %>%
  mutate(
    Trans_Total = ifelse(Variable == "value",Trans_Total/1000000, #million
                         ifelse(Variable == "catch",Trans_Total/1000, #thousand
                                Trans_Total)
                         )
  ) %>% 
  spread(Variable,Trans_Total) %>% 
  # left_join(Entity_Area,
  #           by = "fishing_entity") %>%
  # # Include the weighted method for supplementals
  # mutate_at(
  #   vars(catch,value),
  #   funs(weight= ./(Size_Entity/1000000))
  # ) %>%
  # gather("Variable","Value",catch:value,catch_weight:value_weight) %>%
  gather("Variable","Value",catch:value) %>%
  group_by(fishing_entity,Variable,Value) %>% 
  mutate(
    Bins = cut(Value, breaks = Map_Breaks, dig.lab = 5),
    Bins_Plot = cut(Value, breaks = Map_Breaks,
                    labels = c('super low', 'low','median','high','super high'),
                    dig.lab = 5 # Removes scientific notaion
    )
  ) %>% 
  left_join(Total_Value_EEZ,
            by = c("fishing_entity", "Variable") 
            ) %>% # uncomment for estimating percentage
  # Convert catch to million tonnes
  ungroup() %>% 
  mutate(
    Value = ifelse(Variable == "catch",Value/1000, #million
                         Value),
    Trans_Per = (Value/Total_Value)*100000000 #Return to percentage
  )

@@

Subregion_Trans_raw_Value <- Value_Trans_Country %>% 
  left_join(UN_Regions,
            by = "fishing_entity") %>% 
  mutate(sub_region = ifelse(is.na(sub_region), "Other",paste(sub_region))) %>% 
  group_by(sub_region,Variable) %>% 
  summarise_if(is.numeric,c(sum = sum,
                            m = mean,
                            sd = sd),
               na.rm=T) %>%
  # select(-Size_Entity,-Trans_Entity_n) %>% 
  arrange(Variable) %>%
  ungroup() %>% 
  mutate(id = rep(seq(1,17),2)) %>% 
  mutate(Value_sum=ifelse(Variable == "catch" & Value_sum >= 12,12,Value_sum))

@@

Status_Plot_Data <- tibble(
  fishing_entity = rep(unique(Status_Data_Plot$individual),4),
  observation = rep(unique(Status_Data_Plot$observation),153)
) %>% 
  left_join(UN_Regions) %>% 
  rename(individual = fishing_entity) %>% 
  full_join(Status_Data_Plot,
            by = c("individual","observation")
  ) %>% 
  mutate(value = ifelse(is.na(value),0,
                        ifelse(value < -100,-100, # if less than 100, 100
                               ifelse(value > 100,100, # if more than 100, 100
                                      value)
                        )#, # Ser NAs to 0's
                        # group = ifelse(is.na(group),"Other",group)
  )
  ) %>% 
  select(individual,observation,group=georegion,value) %>% 
  filter(group != "other")

@@

ggsave(
  plot = last_plot(),
  width = 17,
  height = 15,
  units = "in",
  # filename = "Plot.png"
  filename = "Territory_circular_status.png"
)
